Ethereum: A Secure Decentralised Generalised Transaction Ledger

### 2014-04-17 Paper.tex
Incorrect timestamp reference.

The canonical difficulty of a block of header $H$, is defined as $D(H)$:
\begin{equation}
D(H) \equiv \begin{cases}
2^{22} & \quad \text{if genesis block}\\
{P(H)_H}_d + \lfloor\frac{{P(H)_H}_d}{1024}\rfloor & \quad \text{if $H_t < {P(H)_H}_t + 42$}\\
{P(H)_H}_d - \lfloor\frac{{P(H)_H}_d}{1024}\rfloor & \quad \text{otherwise}\\
\end{cases}
\end{equation}

$H_t$ is the timestamp of block $H$, must fulfill the relation:
\begin{equation}
H_t > {P(H)_H}_t
\end{equation}

@@

\section{Recursive Length Prefix}\label{app:rlp}
This is a serialisation method for encoding arbitrarily structured binary data (byte arrays). Within RLP, integers are specified as the byte array equal to the big-endian representation of the value. Thus we may define the notation of a tree structure $\mathbf{t}$:

\begin{equation}
\mathbf{t}
\end{equation}

We define the function $\mathtt{\tiny RLP}$ that maps from an arbitrarily structured tree whose leaves are byte arrays into a single byte array.

>>>>

The canonical difficulty of a block of header $H$, is defined as $D(H)$:
\begin{equation}
D(H) \equiv \begin{cases}
2^{22} & \quad \text{if genesis block}\\
{P(H)_H}_d + \lfloor\frac{{P(H)_H}_d}{1024}\rfloor & \quad \text{if $H_s < {P(H)_H}_s + 42$}\\
{P(H)_H}_d - \lfloor\frac{{P(H)_H}_d}{1024}\rfloor & \quad \text{otherwise}\\
\end{cases}
\end{equation}

$H_s$ is the timestamp of block $H$, must fulfill the relation:
\begin{equation}
H_s > {P(H)_H}_s
\end{equation}

@@

\section{Recursive Length Prefix}\label{app:rlp}
This is a serialisation method for encoding arbitrarily structured binary data (byte arrays). Within RLP, integers are specified as the byte array equal to the big-endian representation of the value.

%Thus we define the set of possible structures $\mathbb{T}$:

%\begin{eqnarray}
%\text{Let} \mathbf{t} & = & \langle \mathbf{t}_0, \mathbf{t}_1, ... \rangle
%\vee \mathbf{t} & = & 
%\end{eqnarray}

%We define the function $\mathtt{\tiny RLP}$ that maps from an arbitrarily structured tree whose leaves are byte arrays into a single byte array.
